The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-10 draft/ms.tex
Add missing references for Sec 2.

{\bf I} is the orbital inclination. Previously, only transiting systems have I measured but now, sometimes, non-transiting systems have I's reported too. ZZZ(add reference) For example, one microlensing system has I measured (OGLE-2006-BLG-109L).

@@

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the Rossiter-McLaughlin
effect or planet transiting star spots ZZZ add references for RM effect and the star spot method. $\lambda$ is introduced because the true spin-orbit angle
($\phi$), defined as the angle between the stellar spin axis and the
orbital axis, is normally not directly measurable. We follow the
definition of $\lambda$ in \cite{Fabrycky2009} where the
coordinates are defined as follows; the $z$-axis points toward the
observer, the $x$-axis points along the intersection of the sky plane
and the planet's orbital plane with the ascending node of the planet
having $x<0$, and the $y$-axis completes a right
handed-triad. $\lambda$ is measured clockwise on the sky from the
$y$-axis to the projected stellar rotational axis. $\lambda$ is not a newly added field but we describe it here because $\lambda$'s were not reported consistently since some literatures
report $\beta = -\lambda$ instead. We sorted these cases out and made
sure that our $\lambda$'s are following the definition of \cite{Fabrycky2009}.

{\bf MASSREF} and {\bf MASSURL} fields were used to report the
reference and the URL of stellar mass but now they are used for planet
mass.
%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

@@

ZZZ RA, DEC, and PAR do not have references but they are from the \textit{Hipparcos} by \cite{van Leeuwen2009}. $B-V$ (BMV) field does not have a reference but the values are from the \textit{Hipparcos} catalog. The fields J H and KS do not have references as well but they are from the 2MASS \citep{Skrutskie2006}. The KP field do not have reference but the values are from the Exoplanet Archive \citep{Akeson2013}.

>>>>

{\bf I} is the orbital inclination. Previously, only transiting
systems have I measured but now, sometimes, non-transiting systems
have I's reported too. For example, one microlensing system has I
measured (OGLE-2006-BLG-109L; \citealt{Bennet2010}).

@@

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the unit of degree. We report the projected spin-orbit misalignment of
transiting systems, which is measured by, e.g., the
Rossiter-McLaughlin effect \citep[e.g.,][]{Winn2005} or planet
transiting star spots \citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is
introduced because the true spin-orbit angle ($\phi$), defined as the
angle between the stellar spin axis and the orbital axis, is normally
not directly measurable. We follow the definition of $\lambda$ in
\cite{Fabrycky2009} where the coordinates are defined as follows; the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field but we describe it here because $\lambda$'s
were not reported consistently since some literatures report $\beta =
-\lambda$ instead. We sorted these cases out and made sure that our
$\lambda$'s are following the definition of \cite{Fabrycky2009}.

{\bf MASSREF} and {\bf MASSURL} fields were used to report the
reference and the URL of stellar mass but now they are used for planet
mass.

%------------------------------------------------------------------------------
\subsection{Transit Parameters}\label{sec:transit}

@@

RA, DEC, and PAR do not have references but they are from the
\textit{Hipparcos} by \cite{van Leeuwen2009}. $B-V$ (BMV) field does
not have a reference but the values are from the \textit{Hipparcos}
catalog by \cite{Perryman1997}. The fields J H and KS do not have
references as well but they are from the 2MASS
\citep{Skrutskie2006}. The KP field do not have reference but the
values are from the Exoplanet Archive \citep{Akeson2013}.

### 2014-03-10 draft/references.tex
Tiny revisions in Sec 2 and ref.
Add missing references for Sec 2.

@@

@@

@@

@@

@@

>>>>

\bibitem[Bennett et al.(2010)]{Bennett2010} Bennett, D.~P., et al.\ 2010, 
\apj, 713, 837 % OGLE microlensing planet with inclination measured

@@

\bibitem[Collier Cameron et al.(2010)]{Collier Cameron2010} Collier 
Cameron, A., et al.\ 2010, \mnras, 407, 507 % WASP-33b having no RV
                                % detection and K upper limit

@@

\bibitem[Johnson et al.(2011)]{Johnson2011} Johnson, J.~A., et al.\ 2011, 
\apjs, 197, 26 % HD 116029B having ECC upper limit (circular orbit)

@@

\bibitem[Perryman \& ESA(1997)]{Perryman1997} Perryman, M.~A.~C., \&
  ESA 1997, ESA Special Publication, 1200 % Hipparcos B-V reference

@@

\bibitem[Sanchis-Ojeda et al.(2012)]{Sanchis-Ojeda2012} Sanchis-Ojeda, R., 
et al.\ 2012, \nat, 487, 449 % Kepler 30 system lambda measurement
                             % with star spot transit

@@

\bibitem[Winn et al.(2005)]{Winn2005} Winn, J.~N., et al.\ 2005, \apj, 631, 
1215 % HD 209458b, the first Rossiter-McLaughlin lambda measurement
